Breanna_Code

### 2022-09-29 Draft_Report.Rmd
some text

>>>>

## view raw data
Note that the raw data contain characters that will make things tricky later on.  I would exclude parenth etc as general practice. Also names are quite long, making it difficult to include in the models.  This is where having a data dicitonary is useful, as you can keep descriptions, formal names, plot names available for use in figures.
